\textsf{Are large language models superhuman chemists?}

### 2024-10-19 src/tex/appendix.tex
add in logprobs figure

>>>>

\clearpage
\subsection{Impact of sampling temperature}
We also investigated the impact of sampling temperature on the performance of the models. \Cref{fig:temperature_impact} shows that, generally, the performance of models tends to degrease with increasing temperature.

\begin{figure}
    \centering
    \includegraphics{figures/swarm_plot_combined.pdf}
    \caption{\textbf{Impact of sampling temperature on the performance of the models.} The plot shows the performance of the models at zero temperature (i.e., greedy decoding) and temperature of one. The performance is measured in terms of the fraction of questions answered correctly.}
    \label{fig:temperature_impact}
    \script{plot_temperature_diffs.py}
\end{figure}
